Model LF

### 2022-10-11 max_dp endogen stød.Rmd
Commit

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

@@

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod= prod_shock
if> shock_prod_model > 0

@@

  ##Sensitivites analyse

  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  ## max_dp

@@

S_modelData$sens2_up = sens2_up

@@

>>>>

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens3_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> Sensitivitets analyse
IDENTITY> sens3_low
EQ> sens3_low = sens3_low*1

@@

COMMENT> 
BEHAVIORAL> prod_shock_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock_sens) = prs_0 + prs_1* TSDELTALOG(TSLAG(prod_shock_sens,2)) + prs_2* TSDELTALOG(TSLAG(prod_shock_sens,3)) + prs_3* TSDELTA(TSLAG(s_h,1))+  prs_4* TSDELTA(TSLAG(s_h,2)) + prs_5* TSDELTA(TSLAG(s_h,3)) + prs_6* TSDELTA(TSLAG(s_h,4))  + prs_8* LOG(TSLAG(dp_person,1)) + prs_9* TSLAG(s_h,1) + prs_10* LOG(TSLAG(prod_shock_sens,1)) 
RESTRICT> prs_8 = 0.1
COEFF> prs_0 prs_1 prs_2 prs_3 prs_4 prs_5 prs_6 prs_8 prs_9 prs_10
STORE> coe(24)

COMMENT> 
IDENTITY> prod
EQ> prod=prodk * (y/yk)
if> shock_prod_model <= 0
IDENTITY> prod
EQ> prod= prod_shock
if> shock_prod_model > 0
IDENTITY> prod
EQ> prod= prod_shock_sens
if> shock_prod_model > 0 & sens3_low >= 0

@@

  ##Sensitivites analyse
  prod_shock_sens = TIMESERIES(c(prod),   
                       START=c(2005,2),FREQ=4),

  sens1_up = TIMESERIES(c(sens1_up),   
                       START=c(2005,2),FREQ=4),
   sens1_low = TIMESERIES(c(sens1_low),   
                       START=c(2005,2),FREQ=4),
  sens2_up = TIMESERIES(c(sens2_up),   
                       START=c(2005,2),FREQ=4),
   sens2_low = TIMESERIES(c(sens2_low),   
                       START=c(2005,2),FREQ=4),
  sens3_low = TIMESERIES(c(sens3_low),   
                       START=c(2005,2),FREQ=4),
  ## max_dp

@@

S_modelData$sens3_low = sens3_low

@@

## Sens 3_low

We change the estimate in prod function to 0.1.

```{r}
# Define add-factor list (defining shock)
constantAdjList_sens3_low <- list(

 sens3_low = TIMESERIES(sens2_low+1 ,START=c(2016,1),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_3_bs_low <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_sens3_low
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_sbs3_low = sens_3_bs_low$simulation$max_dp
wage_sbs3_low = sens_3_bs_low$simulation$wage
komp_r_sbs3_low = sens_3_bs_low$simulation$komp_r
part_sbs3_low = sens_3_bs_low$simulation$part
yk_ds_sbs3_low = sens_3_bs_low$simulation$yk_ds
pc_ds_sbs3_low = sens_3_bs_low$simulation$pc_ds
wage_ds_t_sbs3_low = sens_3_bs_low$simulation$wage_ds_t
pc_ds_sbs3_low = sens_3_bs_low$simulation$pc_ds
max_gap_sbs3_low = sens_3_bs_low$simulation$max_gap
wage_gap1_sbs3_low = sens_3_bs_low$simulation$wage_gap1
inflation_sbs3_low = sens_3_bs_low$simulation$inflation
wage_ds_sbs3_low = sens_3_bs_low$simulation$wage_ds

prod_sbs3_low = sens_3_bs_low$simulation$prod
```

```{r}
# Define add-factor list (defining shock)
constantAdjList1_sens3_low <- list(

 sens3_low = TIMESERIES(sens3_low+1 ,START=c(2016,1),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_3_S1_low <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_sens3_low
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_s3_low = sens_3_S1_low$simulation$max_dp
wage_s3_low = sens_3_S1_low$simulation$wage
komp_r_s3_low = sens_3_S1_low$simulation$komp_r
part_s3_low = sens_3_S1_low$simulation$part
yk_ds_s3_low = sens_3_S1_low$simulation$yk_ds
pc_ds_s3_low = sens_3_S1_low$simulation$pc_ds
wage_ds_t_s3_low = sens_3_S1_low$simulation$wage_ds_t
pc_ds_s3_low = sens_3_S1_low$simulation$pc_ds
max_gap_s3_low = sens_3_S1_low$simulation$max_gap
wage_ds_s3_low = sens_3_S1_low$simulation$wage_ds
wage_gap1_s3_low = sens_3_S1_low$simulation$wage_gap1
wage_gap_s3_low = sens_3_S1_low$simulation$wage_gap

inflation_s3_low = sens_3_S1_low$simulation$inflation

prod_s3_low = sens_3_S1_low$simulation$prod
```

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(0.9, 1.1));
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```
